%Section: Personal Data
\section{\faUser\ Introduction}
Passionate backend and cloud-native software developer with seven years of experience. I specialize in building scalable, cost-efficient and secure solutions on Microsoft Azure, leveraging Infrastructure as Code, CI/CD pipelines, and DevOps best practices like quality gates to enable reliable and automated delivery. Valuing development efficiency, I constantly invest in my work-
flow through the proficient use of terminal tools, keyboard shortcuts, and IDE productivity
features.

Committed to writing high-quality, maintainable code, I take a structured approach to software development. This includes thoroughly tested code using unit, integration, and possibly SpecFlow tests, as well as applying design patterns to create robust, clean, and extensible systems. While my expertise lies in backend and cloud development, I am actively growing my frontend skill set—with technologies like Svelte, Tailwind, and Vue—with the goal to become a full-stack developer.

I’m especially motivated by working on projects with real societal impact—solutions that make the world more sustainable, inclusive, or efficient. I actively engage with end-users and stakeholders to ensure we’re solving the right problems and delivering meaningful outcomes. Known as a sociable and humorous team member, I thrive in knowledge-sharing environments that encourage critical thinking, creativity, and continuous learning—whether through peer mentoring or by attending industry conferences.